Enhancement of SDR in Thessaloniki

### 2024-01-26 GHI_enh_01_raw_data.tex
Commit 2023-11-30 19:12
Commit 2024-01-16 14:15
Commit 2024-01-26 12:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2023-11-27}

@@

\begin{verbatim}
## Written:  ./figures/tbl_tsi_info.dat 
## 
## 
##   Sun Earth distance correction
## 
##   Saved raw input data: ./data/CE_ID_Input.Rds
\end{verbatim}

@@

\begin{verbatim}
2023-11-27 16:57:17.7 athan@sagan GHI_enh_01_raw_data.R 5.129633 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-01-26}

@@

\begin{verbatim}
## Written:  ./figures/tbl_tsi_info.dat 
## 
## 
##   Saved raw input data: ./data/CE_ID_Input.Rds
\end{verbatim}

@@

\begin{verbatim}

2024-01-26 09:51:48.2 athan@sagan GHI_enh_01_raw_data.R 5.347763 mins
\end{verbatim}
